Think deep for reef resilience

### 2025-08-16 paper/paper_draft.qmd
Address bioregion scale comments. Changes were suitable

In contrast to the broad temporal behaviour at the Management area scale, the relationship
between reef characteristics **\[TI: Ben, I think this is what you meant by "contextual
analysis factors"? depth, connectivity, dhw, carrying capacity etc?\]** and reefs' assigned
categories were found to be similar at the bioregion scale **\[TI: Ben, please confirm my
changes/edits are correct\]**. Results are therefore only shown and discussed for
ACCESS-ESM1-5, an intermediate Equilibrium Climate Sensitivity scenario [@sfig-ecs]. Those
interested in results for the other assessed GCMs are referred to Grier and Iwanaga
[-@grier2025]. Across bioregions, reefs in the High category not only had greater levels of
coral recovery but displayed persistence to 2050 [@sfig-access-esm1-5-bioregion-timeseries].
Reefs in the High category were consistently found to have the greatest median reef depths
across bioregions [@fig-access-esm1-5-bioregion-depth].

@@

In many bioregions reefs in the Low category have the lowest correlation between coral cover
and DHW whereas reefs in the High category were found to have the strongest correlation
(@sfig-access-esm1-5-bioregion-dhwcor). Conversely, there are no consistent patterns across
bioregions when comparing their temporal behaviour with respect to their reef area, relative
cover, and mean of DHWs (@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent
differences across bioregions and GCMs between clusters in their reefs' initial proportion
of habitable area occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion).
Across most bioregions there were not consistent differences between clusters in
connectivity metrics such as source-to-sink connectivity ratio
(@sfig-access-esm1-5-bioregion-logsosi) and total connectivity strength
(@sfig-access-esm1-5-bioregion-totalconnectivity).

>>>>

In contrast to the broad temporal behaviour at the Management area scale, the relationship
between reef characteristics and reefs' assigned categories were found to be similar at the
bioregion scale across GCMs. Results are only shown and discussed for ACCESS-ESM1-5, an
intermediate Equilibrium Climate Sensitivity scenario [@sfig-ecs]. Those interested in
results for the other assessed GCMs are referred to Grier and Iwanaga [-@grier2025]. Across
bioregions, reefs in the High category not only had greater levels of coral recovery but
displayed persistence to 2050 [@sfig-access-esm1-5-bioregion-timeseries]. Reefs in the High
category were consistently found to have the greatest median reef depths across bioregions
[@fig-access-esm1-5-bioregion-depth].

@@

In many bioregions reefs in the Low category have the lowest correlation between coral cover
and DHW whereas reefs in the High category were found to have the strongest correlation
(@sfig-access-esm1-5-bioregion-dhwcor). Conversely, there are no consistent patterns across
bioregions when comparing their temporal behaviour with respect to their reef area and mean
of DHWs (@sfig-access-esm1-5-bioregion-dhwmean). There were no consistent differences across
bioregions and GCMs between clusters in their reefs' initial proportion of habitable area
occupied by corals (@sfig-access-esm1-5-bioregion-initialproportion). Across most bioregions
there were not consistent differences between clusters in connectivity metrics such as
source-to-sink connectivity ratio (@sfig-access-esm1-5-bioregion-logsosi) and total
connectivity strength (@sfig-access-esm1-5-bioregion-totalconnectivity).
